Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-13 papers/LREC2020/conclusion.tex
some comments (5 or 6) in LREC paper

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object recognition and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.

>>>>

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous \sz{does the data presented here really do this?}, which can affect model performance on object recognition and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.\sz{well, this paper does not contain the verification data right=}

### 2020-03-13 papers/LREC2020/data-collection.tex
updates distr plot; updates lrec style file
some comments (5 or 6) in LREC paper

\begin{figure}[htp]
	\centering
	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VGMN.png}
	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure}

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round1+_p1.png}
  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}
  \label{fig:instructions2}
\end{figure*}

>>>>

\begin{figure*}[htp]
	\centering
	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN.png}
	\caption{Cumulative histograms of the number of images and \sz{original VG?} names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=1\columnwidth]{figures/round1+_p1.png}
  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}
  \label{fig:instructions2}
\end{figure*}

### 2020-03-13 papers/LREC2020/intro.tex
some comments (5 or 6) in LREC paper

% GBT revision:
In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
%We start by surveying existing resources in L\&V that provide object names, assessing their potential to contribute to the study of object naming.
%While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
We chose a creation methodology for ManyNames to overcome these shortcomings in particular.
%This motivates the development of ManyNames, as well as our design choices for it.

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames~v.1 contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~\cite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

>>>>

% GBT revision:
In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
%We start by surveying existing resources in L\&V that provide object names, assessing their potential to contribute to the study of object naming.
%While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other. 
We chose a creation methodology for ManyNames to \sz{sounds slightly weird, a methodology that ... ???}overcome these shortcomings in particular.
%This motivates the development of ManyNames, as well as our design choices for it.

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames~v.1 contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in \sz{by?} picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~\cite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

### 2020-03-13 papers/LREC2020/lrec2020naming.tex
some comments (5 or 6) in LREC paper

\section{Object Names in Existing L\&V Resources}
\label{sec:survey}
\input{survey}

@@

\section{Acknowledgments}
We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
 This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154), from the Ramón y Cajal programme~(grant RYC-2015-18907), and by the Catalan government~(SGR 2017 1575).
 % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
 This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
 \hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
% Place all acknowledgements (including those concerning research grants and
% funding) in a separate section at the end of the article.

>>>>

\section{Object Names in Existing L\&V resources}
\label{sec:survey}
\input{survey}

@@

%\section{Acknowledgements}

% Place all acknowledgements (including those concerning research grants and
% funding) in a separate section at the end of the article.

### 2020-03-13 papers/LREC2020/survey.tex
adds logos
updates distr plot; updates lrec style file
some comments (5 or 6) in LREC paper

Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object. 
The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

>>>>

Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object. 
The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use certain \sz{only left and right were forbidden, east and west are allowed ;-)} location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
